\part{Conclusion}
\section{Reflection on goals}
I set three targets when I started my internship; improve my skills in programme design, improve my time management skills, and improve my presentation skills.
    \subsection{Improve my skills in programme design} Most of my deliverables at Surewash involved code, which was predominantly Python. Having started with very little exposure to Python, I now feel confident reading and writing Python code. I have also gained experience with the soft skills of Python, such as what libraries are available, which means that I can now make a more informed decision as to what development path to take if I am given a new problem to solve using Python.

    As well as Python, I also produced deliverables in C, C sharp, and Java, which has improved my understanding of those languages.

    Other important skills that I learned in programme design are learning about using a debugger, exception handling, interprocess communication, and threaded programming.

    \subsection{Improve my time management skills} I set this goal as I feel that it is an important skill to have, and not really something that I would have had to worry about while in university to the same extent that I would in a commercial environment. In a professional environment, the more time spent on a project, the more money it will cost. I think that I improved my time management skills by learning about how certain tools can be used to accelerate my workflow, these tools weren't core to my work, but they did make things easier. As an example, in the project on neural networks, I used an AWS server to train the neural network, since that was faster than doing it locally, but due to cost constraints, any extra data processing was still done on my own computer. The problem was that when I had finished preparing a dataset to train on the AWS server, it took a considerable amount of time just to upload the data, and there wasn't any other task that I could complete in the meantime, but using 7-Zip reduced the file size, and therefore the time spent uploading the file.

    \subsection{Improve my presentation skills and public speaking skills} Given my experience at the start of my time at Surewash, I anticipated that I would continue to make presentations to my work colleagues, but this turned out not to be the case, and therefore I didn't gain the experience I had hoped for in this. I did improve my presentation skills however in documenting my work. Typically at the conclusion of a project, I would be asked to write a document describing how my solution works, both from a technical, and non-technical perspective.

\section{Other reflection}
The whole experience of stepping away from lectures and into a commercial setting has given me a whole host of experiences that I simply would not have been able to attain in an educational environment. Aside from the technical learning outcomes of this internship, probably the most important thing that I learned was applying for a job. From writing a cv, to attending interviews, and dealing with rejection, this experience alone has been invaluable to me. Due to the nature of what Surewash does, I learned a lot about hand hygiene, and I would consider myself proficient at the WHO hand washing method.

\section{Postscript}
Every Friday at lunch, all of the office participated in the Joe.ie pub quiz, I usually found myself strong on history, politics, and geography, but comparatively weak on topics such as music and sport.

I learned a lot about coffee making, due to the presence of a coffee grinder. During breaks, I had the opportunity to try various methods of coffee making, as well as coffee types. This ended badly one day when I accidently broke my cafetiere and subsequently found myself in Accident and Emergency with an uncontrollably bleeding thumb due to the broken glass, it has since recovered.

For a period of about three weeks in June, the office played host to a fly who was affectionatly called Bartholomew. Despite best efforts, we failed to get rid of the fly, he disappeared in mysterious circumstances one day.